Introduction

### 2018-05-03 abs.tex
thesis updated
thesis almost done

Data matching applications are present in many computational geophysics problems.
In this thesis, I introduce a new algorithm to aid in data matching that balances local frequency content between seismic data sets.
Then, I provide a few examples where applying this algorithm to seismic data helps improve results.
These applications include multi-component image registration, matching and merging high-resolution and legacy seismic images, and improving migration resolution by approximating the least-squares Hessian.
The applications are applied to several 2D and 3D, real and synthetic data sets.

>>>>

\author{Sarah Greer, The University of Texas at Austin}
\title{Abstract}
\label{ch:abs}

Data matching applications appear in many computational geophysics problems.
In this thesis, I introduce a new efficient algorithm to aid in data matching that balances local frequency content between seismic data sets.
Then, I provide a few examples where applying this algorithm to seismic data helps improve results.
These applications include multi-component image registration, matching and merging high-resolution and legacy seismic images, and improving migration resolution by approximating the least-squares Hessian.
The applications are illustrated by several 2D and 3D, real and synthetic data sets.

### 2018-05-03 ack.tex
thesis almost done

I would especially like to thank the members of the Texas Consortium for Computational Seismology (TCCS), of which I have been a part for the past two years.
%Thank you for all your guidance, and for being there for the best memories during my undergraduate career.
%Thank you for your intellectually stimulating conversations, life advice, and making me feel as though I am ``part of the group'', despite the fact that I was not a graduate student.
Thank you all for your intellectually stimulating conversations, life advice, and for including me as ``part of the group'', despite the fact that I was only an undergraduate student.
%You are an incredibly enjoyable and intellectually stimulating group, and I am glad I have had the opportunity to cross paths with all of you in life.
I will forever cherish the friendships and memories I have made with all of you during my time as a part of TCCS. %Many of the best memories of my time at UT Austin are from being a part of TCCS, %come from the %time I have spent as a part of TCCS.
You are an incredibly ingenuitive and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.

>>>>

I would especially like to thank the members of the Texas Consortium for Computational Seismology (TCCS), of which I have been a part for the past two years.
%Thank you for all your guidance, and for being there for the best memories during my undergraduate career.
%Thank you for your intellectually stimulating conversations, life advice, and making me feel as though I am ``part of the group'', despite the fact that I was not a graduate student.
Thank you all for your intellectually stimulating conversations, life advice, and for including me as ``part of the group'', despite the fact that I was only an undergraduate student.
%You are an incredibly enjoyable and intellectually stimulating group, and I am glad I have had the opportunity to cross paths with all of you in life.
I will forever cherish the friendships and memories I have made with all of you during my time as a part of TCCS. %Many of the best memories of my time at UT Austin are from being a part of TCCS, %come from the %time I have spent as a part of TCCS.
%You are an incredibly ingenuitive and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.
You are an incredibly bright and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.

### 2018-05-03 chapter-background/paper.tex
thesis almost done

\title{Background}
\author{Sarah Yvonne Greer}
\maketitle
\inputdir{../chapter-locfreq/merge}
Seismic data contain fundamentally non-stationary variations in attributes such as frequency and amplitude content.
For example, Figure \ref{fig:legacy,low-freq} shows a sample seismic image and its local frequency content \cite[]{locfreq}.
%Non-stationary, or spatially and temporally variant, changes in these data can make the comparison of two data sets difficult.
%These non-stationary variations mean that, in a given data set, different 
Data matching problems involve finding some transformation, or set of transformations, that can be applied to one data set to best match some attribute with another data set.
In data matching applications, in particular, it is crucial to acknowledge the non-stationary variations present in seismic data.
Therefore, any transformations we might apply in a data matching problem must be variant in all data dimensions to account for these non-stationary variations.

Local seismic attributes are useful in the analysis of these non-stationary variations that are naturally present in seismic data \cite{attr}.
The calculation of these attributes uses iterative inversion with shaping regularization \cite{shap} to measure signal characteristics in local regions of data, rather than specifying windows or looking at instantaneous attributes.
For the procedures described in this thesis, local attributes are more appropriate than instantaneous attributes.
Take, for example, local frequency (Figure \ref{fig:legacy,low-freq}), as opposed to instantaneous frequency.
Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images. 
Because the corresponding reflections between images might not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency. 
Additionally, local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or extremely high frequency values \cite[]{attr}.

\multiplot{2}{legacy,low-freq}{width=0.47\columnwidth}{A seismic image (a) and its local frequency content (b). Because its local frequency varies both spatially and temporally, we can say its frequency content is {\it non-stationary}.}

@@

%These applications can be solved by specifying and applying the three previously stated data matching operators: filtering, scaling, and shifting.
To demonstrate the three matching operations in action, I apply them consecutively to an example 2D trace shown in Figure \ref{fig:one0}.
The data used in this example comes from a line from the {\em P-cable} data sets.
In this example, we want to find a transformation, or a set of transformations, to apply to the red trace to match with the black trace.
I use the three data matching operators by first filtering (Figure \ref{fig:one1}), then scaling (Figure \ref{fig:one2}), and finally shifting (Figure \ref{fig:one3}).
The three operations are described in more detail in the following sections.

@@

\section{Filtering}
Perhaps one of the most visibly obvious differences between data sets comes from differences in frequency content.
For example, Figure \ref{fig:one0} shows two traces that need to be matched; the red trace has visibly higher frequency content than the black trace which makes it difficult to observe that they may both contain data from the same model.
This makes the correlation of these two signals, both visually and computationally, difficult as they have information in different frequency bands.
In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content with the black trace because the high frequency content is not physically present in the black trace.

@@

We instead do this by applying a non-stationary triangle smoothing operator to the red trace to match local frequency content with the black trace.
We define the {\em radius} of this operator as the number of samples in a specified dimension that are averaged over in a triangle weight.
We allow the radius to vary in all dimensions to account for the potential non-stationary frequency variations present in the data.
This is a linear operation---if we represent the filtering operation by a matrix applied to the trace represented by a vector, the matrix would be diagonally banded, where the size of the band at a particular index is related to the size of the smoothing radius at that point.

@@

\section{Scaling}
The second primary data matching operation is scaling. 
Amplitudes of the data we are trying to match may not be initially correct---scaling attempts to balance the amplitudes between these data.
Scaling is also a linear operation and can be thought of as a diagonal operation; if the scaling operator is represented by a matrix multiplication to the data vector, this matrix only contains terms along the diagonal.

In this thesis, the diagonal scaling operator is found by first calculating the amplitude envelope of the data that need to be matched.
Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces and represents the diagonal elements of the scaling operator.
%The result of

>>>>

\title{Background}
\author{Sarah Yvonne Greer}
\label{ch:chapter-background}

\maketitle
\inputdir{../chapter-locfreq/merge}
Seismic data exhibit fundamentally non-stationary variations in attributes such as frequency and amplitude content.
For example, Figure \ref{fig:legacy,low-freq} shows a sample seismic image and its local frequency content \cite[]{locfreq}.
%Non-stationary, or spatially and temporally variant, changes in these data can make the comparison of two data sets difficult.
%These non-stationary variations mean that, in a given data set, different 
Data matching problems involve finding some transformation, or set of transformations, that can be applied to one data set to best match some attribute with another data set.
In data matching applications, in particular, it is crucial to acknowledge the non-stationary variations present in seismic data.
Therefore, any transformations we might apply in a data matching problem must be variant in all data dimensions to account for these non-stationary variations.

Local seismic attributes are useful in the analysis of these non-stationary variations \cite[]{attr}.
The calculation of these attributes uses iterative inversion with shaping regularization \cite[]{shap} to measure signal characteristics in local regions of data, rather than specifying windows or looking at instantaneous attributes.
For the procedures described in this thesis, local attributes are more appropriate than instantaneous attributes.
Take, for example, local frequency (Figure \ref{fig:legacy,low-freq}), as opposed to instantaneous frequency.
Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which attempts to provide a point by point comparison of frequency values between images. 
Because the corresponding reflections between images might not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency. 
Additionally, local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or unrealistic high frequency values \cite[]{attr}.

\multiplot{2}{legacy,low-freq}{width=0.47\columnwidth}{A seismic image (a) and its local frequency content (b). Because its local frequency varies both spatially and temporally, we can say its frequency content is smoothly {\it non-stationary}.}

@@

%These applications can be solved by specifying and applying the three previously stated data matching operators: filtering, scaling, and shifting.
To demonstrate the three matching operations in action, I apply them consecutively to an example trace shown in Figure \ref{fig:one0}.
The data used in this example comes from a line from the {\em P-cable} data sets.
In this example, we want to find a transformation, or a set of transformations, to apply to the red trace to match with the black trace.
I use the three data matching operators by first filtering (Figure \ref{fig:one1}), then scaling (Figure \ref{fig:one2}), and finally shifting (Figure \ref{fig:one3}).
These three operations are described in more detail in the following sections.

@@

\section{Filtering}
Perhaps one of the most visibly obvious differences between data sets comes from their difference in frequency content.
For example, Figure \ref{fig:one0} shows two traces that need to be matched; the red trace has visibly higher frequencies than the black trace which makes it difficult to observe that they may both contain data from the same model.
This makes the correlation of these two signals, both visually and computationally, difficult as they have information in different frequency bands.
In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content of the black trace.
%because the high frequency content is not physically present in the black trace.

@@

We can do this by applying a non-stationary triangle smoothing operator to the red trace to match the local frequency content of the black trace.
We define the {\em radius} of this operator as the number of samples in a specified dimension that are averaged over in a triangle weight.
We allow the radius to vary in all dimensions to account for the potential non-stationary frequency variations present in the data.
This is a linear operation---if we represent the filtering operation by a matrix applied to the trace represented by a vector, the matrix would be diagonally banded, where the width of the band at a particular index is related to the size of the smoothing radius at that point.

@@

\section{Scaling}
The second primary data matching operation is scaling. 
Amplitudes of the data we are trying to match may not be initially equivalent---scaling attempts to balance the amplitudes between these data.
Scaling is also a linear operation and can be thought of as a diagonal operation; if the scaling operator is represented by a matrix multiplication to the data vector, this matrix only contains terms along the diagonal.

In this thesis, the diagonal scaling operator is found by first calculating the amplitude envelope of the data that need to be matched.
Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces to find the diagonal elements of the scaling operator.
%The result of

### 2018-05-03 chapter-conclusion/paper.tex
thesis almost done

\title{Conclusions}
\author{Sarah Yvonne Greer}
\maketitle

@@

The scripts and programs used to produce the examples in this thesis are below.

\definecolor{mygreen}{rgb}{0,0.5,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.5,0,0.8}
\definecolor{c0}{rgb}{0.71,0.54,0}
\definecolor{c1}{rgb}{0.75,0.29,0.09}
\definecolor{c2}{rgb}{0.80,0.20,0.18}
\definecolor{c3}{rgb}{0.15,0.54,0.82}
\definecolor{c4}{rgb}{0.52,0.60,0}
\definecolor{c5}{rgb}{0,0.5,0}
\lstset{ 
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\scriptsize\ttfamily,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  commentstyle=\color{c5},    % comment style
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  language=Python,                 % the language of the code
  deletecomment={[s]{'''}{'''}},
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{c2},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  keywords=[1]{from,for,if,in,import},
  keywords=[2]{Flow,Fetch},
  keywords=[3]{Result,Plot},
  keywordstyle={\color{c0}},
  keywordstyle=[2]{\color{blue}},
  keywordstyle=[3]{\color{c3}},
}
%\lstset{language=python,numbers=left,numberstyle=\tiny,showstringspaces=false}

\begin{table}[h]
\centering
\caption{Figures and the scripts to generate them}
\label{my-label}
\begin{tabular}{l|l|l}
\hline
        \textbf{Figures} & \textbf{Directory} & \textbf{Listings} \\ \hline 
        \ref{fig:legacy,low-freq} & chapter-locfreq/merge/ & \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
        \ref{fig:one0,one1,one2,one3}, \ref{fig:bef,aft} & chapter-background/dmExample/ & \ref{lst:dm} \\ 
        \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, \ref{fig:freqdif,freqdif-filt}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
        \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, \ref{fig:freqdif,freqdif-filt5}          & chapter-locfreq/merge/ &   \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
        \ref{fig:pp,ss}, \ref{fig:before,after}         & chapter-locfreq/vecta/&  \ref{lst:lvs}, \ref{lst:lvn}, \ref{lst:lvrp}, \ref{lst:lvrc}\\ 
        \ref{fig:all,scalar} & chapter-locfreq/convergence/&  \ref{lst:conv}\\ 
        \ref{fig:legacy,hires,merge2-reverse}, \ref{fig:diff0,diff1}, \ref{fig:hweight,lweight-reverse}, \ref{fig:nspectra22-reverse}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
        \ref{fig:window1,window2}, \ref{fig:nspectra2} & chapter-merge/pcable/ & \ref{lst:mps} \\ 
        \ref{fig:legacy4,hires4,merge3}  & chapter-merge/pcable2/ & \ref{lst:mp2s}, \ref{lst:mp2rp}, \ref{lst:mp2rc}\\ 
        \ref{fig:mod,vel-migration}, \ref{fig:image0,image1}, \ref{fig:a0,rect10b}, \ref{fig:migdec-shap}, \ref{fig:image0-w3,migdec-w3,mod-w3} & chapter-merge/mighes/ & \ref{lst:hss}, \ref{lst:hsrp}, \ref{lst:hsrc}\\ 
        \ref{fig:tf}, & chapter-merge/triop/ & \ref{lst:triop}, \ref{lst:trfu} \ref{lst:solve}\\ 
\end{tabular}
\end{table}
For brevity in this thesis, code is only included for one example of the main frequency balancing algorithm presented in chapter 3.

>>>>

\title{Conclusions}
\author{Sarah Yvonne Greer}
\label{ch:chapter-conclusion}

\maketitle

@@

For brevity in this thesis, code is only included for one example of the main frequency balancing algorithm presented in chapter 3.
The code for the rest of the examples in this thesis are available online at the URL above.
%The code for the rest of the examples in this thesis is available online at the URL above.

%The scripts and programs used to produce the examples in this thesis are below.

\definecolor{mygreen}{rgb}{0,0.5,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.5,0,0.8}
\definecolor{c0}{rgb}{0.71,0.54,0}
\definecolor{c1}{rgb}{0.75,0.29,0.09}
\definecolor{c2}{rgb}{0.80,0.20,0.18}
\definecolor{c3}{rgb}{0.15,0.54,0.82}
\definecolor{c4}{rgb}{0.52,0.60,0}
\definecolor{c5}{rgb}{0,0.5,0}
\lstset{ 
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\scriptsize\ttfamily,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  commentstyle=\color{c5},    % comment style
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  language=Python,                 % the language of the code
  deletecomment={[s]{'''}{'''}},
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{c2},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  keywords=[1]{from,for,if,in,import,def},
  keywords=[2]{Flow,Fetch},
  keywords=[3]{Result,Plot},
  keywordstyle={\color{c0}},
  keywordstyle=[2]{\color{blue}},
  keywordstyle=[3]{\color{c3}},
}
%\lstset{language=python,numbers=left,numberstyle=\tiny,showstringspaces=false}

\begin{table}[h]
\centering
\caption{Figures and the scripts to generate them}
\label{my-label}
\begin{tabular}{l|l|l}
\hline
        \textbf{Figures} & \textbf{Directory} & \textbf{Listings} \\ \hline 
        \ref{fig:legacy,low-freq} & chapter-locfreq/merge/ & \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
        \ref{fig:one0,one1,one2,one3}, \ref{fig:bef,aft} & chapter-background/dmExample/ & ---\\%\ref{lst:dm} \\ 
        \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, \ref{fig:freqdif,freqdif-filt}           & chapter-merge/apache/ & ---\\%\ref{lst:mas} \\ 
        \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, \ref{fig:freqdif,freqdif-filt5}          & chapter-locfreq/merge/ &   \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
        \ref{fig:pp,ss}, \ref{fig:before,after}         & chapter-locfreq/vecta/&  --- \\%\ref{lst:lvs}, \ref{lst:lvn}, \ref{lst:lvrp}, \ref{lst:lvrc}\\ 
        \ref{fig:all,scalar} & chapter-locfreq/convergence/&  --- \\%\ref{lst:conv}\\ 
        \ref{fig:legacy,hires,merge2-reverse}, \ref{fig:diff0,diff1}, \ref{fig:hweight,lweight-reverse}, \ref{fig:nspectra22-reverse}           & chapter-merge/apache/ & --- \\% \ref{lst:mas} \\ 
        \ref{fig:window1,window2}, \ref{fig:nspectra2} & chapter-merge/pcable/ & --- \\%\ref{lst:mps} \\ 
        \ref{fig:legacy4,hires4,merge3}  & chapter-merge/pcable2/ &  --- \\%\ref{lst:mp2s}, \ref{lst:mp2rp}, \ref{lst:mp2rc}\\ 
        \ref{fig:mod,vel-migration}, \ref{fig:image0,image1}, \ref{fig:a0,rect10b}, \ref{fig:migdec-shap}, \ref{fig:image0-w3,migdec-w3,mod-w3} & chapter-merge/mighes/ & --- \\%\ref{lst:hss}, \ref{lst:hsrp}, \ref{lst:hsrc}\\ 
        \ref{fig:tf}, & chapter-merge/triop/ & --- \\%\ref{lst:triop}, \ref{lst:trfu} \ref{lst:solve}\\ 
\end{tabular}
\end{table}

### 2018-05-03 chapter-intro/paper.tex
thesis almost done

\title{Introduction}
\author{Sarah Yvonne Greer}
\maketitle

%Data matching problems are prevalent in many applications of seismic data processing.
Data matching is a conceptually simple problem that is present in many computational geophysics applications. 
Essentially, given two data sets, data matching can be thought of as finding the transformation from one data set to the other. 
This is useful in applications such as multi-component seismic image registration, where two separate seismic images, one P-wave image and one S- wave image, are acquired over the same area. 
These must be matched properly, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted. 
%Many other examples of data matching are prevalent in geophysical applications, such as time-lapse image registration, seismic and well-log tying, deconvolution, and surface-related multiple elimination.

Many other geophysics applications can be addressed from a data matching standpoint and fall under a few main categories.
Applications are present for data of different physics, such as tying synthetic seismograms from well log data to surface seismic data \cite[]{herrera, bader} and multicomponent seismic image registration \cite[]{multi,warp,hardage}, which is discussed in chapter 3.
Other problems consist of matching differently acquired data, such as time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in chapter 4.
Data matching problems are also present for matching data and ideal models, such as in deconvolution or approximating the inverse Hessian to improve migration resolution \cite[]{migdec,rtmmf,mighess}, which is discussed further in chapter 5.
An approach to these many data matching problems is to find the operation to match the data using a combination of three data matching operations---filtering, scaling, and shifting.
%In this thesis, I will outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
In this thesis, I will discuss these three data matching operators, outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.

%However, many data matching algorithms, such as Dynamic Time Warping, can be computationally expensive, especially when applied to large multi-dimensional seismic data sets.
The primary inspiration for much of the work in this thesis comes from the example of matching and merging high-resolution and legacy seismic images, as discussed in \cite{merge2} and \cite{merge}.
In this example, two seismic data sets, each acquired over the same area but with different technologies, are first matched in frequency, amplitude, and time, before being merged together to produce a third image.
This new image includes the best signal characteristics from the two initial images while minimizing their weaknesses.
Much of the theory behind Chapter 3 was developed in application to this example but was later extended to other examples.
As a result, I use data from this application throughout much of this thesis.

This thesis contains two primary data sets to which I refer. 
The first pair, henceforth called the {\it Apache} data sets, are two 2D lines, acquired over the same area but with different methods, from the Gulf of Mexico. 
These two images will always be plotted in the {\em seismic} color map.

The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable,data}.
These two images will always be plotted in grayscale.
In parts of this thesis, I show a 2D line from this 3D data set for simplicity of plotting.

Two other data sets, both 2D, were used in this paper. 
In chapter 3, I use two multi-component images to demonstrate an adaptation for the proposed frequency balancing algorithm in an application of multi-component image registration \cite[]{attr}.
In chapter 5, I use the Sigsbee synthetic data set \cite[]{sigsbee} in the application of improving migration resolution using non-stationary matching.

This thesis is organized as follows.
In the second chapter, I overview the basics behind the three data matching operations---scaling, shifting, and filtering.
In chapter three, I introduce two methods for balancing local frequency content in seismic data sets.
In the fourth chapter, I show the first example of data matching---matching and merging high-resolution and legacy seismic images.
In the chapter five, I show an example of data matching to improve migration resolution.
Finally, in chapter six, I provide concluding remarks.

>>>>

\title{Introduction}
\author{Sarah Yvonne Greer}
\label{ch:chapter-intro}

\maketitle

Data matching is a conceptually simple problem that appears in many computational geophysics applications. 
Essentially, given two data sets, data matching can be thought of as finding the transformation from one data set to the other. 
This is useful in applications such as multi-component seismic image registration, where two separate seismic images, one P-wave image and one S- wave image, are acquired over the same area. 
These must be matched properly, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted.

Many other geophysics applications can be addressed from a data matching standpoint and fall under several main categories.
One category is matching data of different physics, such as tying synthetic seismograms from well log data to surface seismic data \cite[]{herrera, bader} and multicomponent seismic image registration \cite[]{multi,warp,hardage}, which is discussed in Chapter \ref{ch:chapter-locfreq}.
Another category involves matching differently acquired data, such as time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in Chapter \ref{ch:chapter-merge}.
The third category is matching data and ideal models, such as in deconvolution or approximating the inverse Hessian to improve migration resolution \cite[]{migdec,rtmmf,mighess}, which is discussed further in Chapter \ref{ch:chapter-mighes}.
The objective of these many data matching problems is to approximate the operation to match the data using a combination of three data matching operations---filtering, scaling, and shifting.
%In this thesis, I will outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
In this thesis, I discuss these three data matching operators, outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.

%However, many data matching algorithms, such as Dynamic Time Warping, can be computationally expensive, especially when applied to large multi-dimensional seismic data sets.
The primary inspiration for much of the work in this thesis comes from the example of matching and merging high-resolution and legacy seismic images, as discussed by \cite{merge2, merge}.
In this example, two seismic data sets, each acquired over the same area but with different acquisition technologies, are first matched in frequency, amplitude, and time, before being merged together to produce a third image.
This new image includes the best signal characteristics from the two initial images while minimizing their comparative weaknesses.
Much of the theory behind Chapter \ref{ch:chapter-locfreq} was developed in application to this example but was later extended to other examples.
Therefore, I data from this application throughout much of this thesis.

\section{Data}
This thesis refers to two primary data sets. 
The first pair, henceforth called the {\it Apache} data sets, are two 2D lines, acquired over the same area but with different methods, from the Gulf of Mexico. 
These two images are plotted in the {\em seismic} color map, as in Figure \ref{fig:legacy,hires}.

The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets, but also in the Gulf of Mexico \cite[]{pcable,data}.
These two images will always be plotted in grayscale, as in Figure \ref{fig:legacy,hires-agc}.
In parts of this thesis, I show a 2D line from this 3D data set for simplicity of illustration.

Two other data sets, both 2D, were used in this paper. 
In Chapter \ref{ch:chapter-locfreq}, I use two multi-component images to demonstrate an adaptation for the proposed frequency balancing algorithm in an application of multi-component image registration \cite[]{attr}.
In Chapter \ref{ch:chapter-mighes}, I use the Sigsbee synthetic data set \cite[]{sigsbee} in the application of improving migration resolution using non-stationary matching.

\section{Outline}
This thesis is organized as follows.
In Chapter \ref{ch:chapter-background}, I overview the theory behind the three data matching operations---scaling, shifting, and filtering.
In Chapter \ref{ch:chapter-locfreq}, I introduce two methods for balancing local frequency content in seismic data sets.
In Chapter \ref{ch:chapter-merge}, I show the first example of data matching: matching and merging high-resolution and legacy seismic images.
In Chapter \ref{ch:chapter-mighes}, I show an example of applying data matching to improve migration resolution.
In Chapter \ref{ch:chapter-conclusion}, I provide concluding remarks.
Finally, in the appendix, I include information on how to reproduce the results of this thesis.
